\fontsize{14}{14}Bachelor Thesis \\ in \\Allgemeine Informatik \fontsize{22}{22}\textbf{Transhumanism}\\ \fontsize{18}{18} The New Human

### 2014-01-16 draft.tex
Done

\chapter{From the Brain to the Singularity}
  \section{The Superintelligence}
    \subsection{From the Brain to the Computer to the Superbrain}
      \begin{par}
        Moore's law is an often cited observation made in the 60' about the progress of Computer Power. 
        More specifically, Moore stipulated that the number of transistors on integrated circuits doubles approximately every two years. 
        It can be shown that this observation holds true since it has been brought forward.
        This has several implications for future forecasts. 
        One can imagine that through ever progressing technical knowledge a critical amount of calculations per second can be achieved.
        This critical amount would be the equivalent of the human brain.
        We are after all limited through the size and amount of neurons that our brain is made out of.
        This now intelligent Computer could himself design an even more intelligent design or programm of himself.
        Thus, given enough time and energy the intelligence evolves into a superintelligence.
        This process is called the technological singularity due to the unknown factor of what will happen to humankind.
      \end{par}
      \begin{par}
        However there are several hurdles to what will make this intelligence work.
      \end{par}
      \subsubsection{The Program}
        A human, or several, will have to write the program. 
        Which means that it will inherently describe features of humankind.
        This can already be noted today with what is called \emph{Biomimicry}: Humans look at nature and try to replicate it.
        However, many problems arise with this. 
        For one, as Humans we have flaws and these flaws could be very well exacerbated by applying it to a higher machine.
        The problem is also that the same way Chimps cannot understand what we say or do, a superintelligent Computer might be useless to us.
      \subsubsection{The Infrastructure}
        Power today is an important resource, and with the rise of ever faster Computers, this demand for power will rise even more.
        The fastest computer as of today, the Tianhe-2 uses about 20 MW of power per hour. 
        When scaled further up, there will have to be progress for it to be sustainable.
    \subsection{Powering and Nurturing the Computer}
      \begin{par}

        Explain here the technological difficulties of powering and supplying data to such a Computer

      \section{Harnessing the Torrent of Information}
    \subsection{Possible ways to Control the Singularity}
      \begin{par}

        Explain how we humans could control something that is intelligenter than us

>>>>

\chapter{From the Brain to the Singularity}
  \section{The Superintelligence}
    \subsection{From the Brain to the Computer to the Superbrain}
      \begin{par}
        Moore's law is an often cited observation made in the 60' about the progress of Computer Power. 
        More specifically, Moore stipulated that the number of transistors on integrated circuits doubles approximately every two years. 
        It can be shown that this observation holds true since it has been brought forward.
        This has several implications for future forecasts. 
        One can imagine that through ever progressing technical knowledge a critical amount of calculations per second can be achieved.
        This critical amount would be the equivalent of the human brain.
        We are after all limited through the size and amount of neurons that our brain is made out of.
        This now intelligent Computer could himself design an even more intelligent design or programm of himself.
        Thus, given enough time and energy the intelligence evolves into a superintelligence.
        This process is called the technological singularity due to the unknown factor of what will happen to humankind.
      \end{par}
      \begin{par}
        However there are several hurdles to what will make this intelligence work.
      \end{par}
      \subsubsection{The Program}
        A human, or several, will have to write the program. 
        Which means that it will inherently describe features of humankind.
        This can already be noted today with what is called \emph{Biomimicry}: Humans look at nature and try to replicate it.
        However, many problems arise with this. 
        For one, as Humans we have flaws and these flaws could be very well exacerbated by applying it to a higher machine.
        The problem is also that the same way Chimps cannot understand what we say or do, a superintelligent Computer might be useless to us.
      \subsubsection{The Infrastructure}
        Power today is an important resource, and with the rise of ever faster Computers, this demand for power will rise even more.
        The fastest computer as of today, the Tianhe-2 uses about 20 MW of power per hour. 
        When scaled further up, there will have to be progress for it to be sustainable.
  \section{Harnessing the Torrent of Information}
    \subsection{Possible ways to Control the Singularity}
      \begin{par}
        Controlling something intelligenter than us seems to be a logical contradiction, after all if a chimp can't control us how could we control a superintelligence?
        However to answer this we do not have to go to the levels of a superintelligence, instead one could look how we manage with fellow humans.
        The idea of control becomes obselete once a somewhat complete form intelligence exists.
        As is true with many things, intelligence does have a gradual step to it.
        A fish is able to learn from being attacked by a certain animal that it will die if that happens again.
        However, while we use the word \emph{die} as a way to get our point across it is not true that the fish truly knows what death is.
        Humans are the only species able to clearly recognize that we will die at some point.
        We are thus making preparations almost the whole of our live.
        One cannot thus compare a chimp and a human and thus deduce what will happen between a human and a superintelligence.
        It is however clear that some aspects might escape us.
        The same way that a man who lived two hundred years ago did not have the necessary thought processes to imagine something fictional as true to draw conclusions, our current generation may have trouble understanding a superintelligence.
        There is also no doubt that if we can, at some point understand this superintelligence, then we will.\cite{FutureMinds}
      \end{par}
